---
title: "In Class Lab - DIY Functions"
author: "Angelica Gamboa"
date: "DATA 2401"
output: html_document
---
**Note: Your exam will be in a similar format to this (RMarkdown File with Questions and Code chunks for your answers), so make sure you have the process for knitting to html working.** 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## In Class Activity 
The questions from your notes today are below, please copy your answers them here! Then complete the two new tasks, and attempt the "hard mode" if you have time. 

1. Write your own function that takes the temperature in Fahrenheit as an argument and returns the Celcius equivalent. 

```{R}
Fahrenheit_to_Celcius <- function(fahreinheit) {
  celcius <- (fahreinheit - 32)*5/9
  return(celcius)
}

#Test
Fahrenheit_to_Celcius(40)
```

2. Expand that function so that it takes a temperature in Fahrenheit and a distance in feet and returns **both** the temperature in Celcius and the distance in meters (you'll likely need to remember the `c()` function!)


```{r}
expanding_function <- function(fahreinheit,distance) {
  celcius <- (fahreinheit - 32)*5/9
  meters <- distance*0.3048
  return(c(celcius,meters))
}
  
#Test
expanding_function(212,3)

```


3. Write a function that prints out a statement of whether the number passed as an argument is positive, negative or 0. 

```{R}
checking_num <- function(num) {
  if(num < 0) {
    print("Negative number") 
  }else if (num > 0) {
    print("Positive number")
  }else {
    print("Number is zero.")
  }
}

#Test
checking_num(15)

```

4. Write a function that returns the absolute value of the number passed as an argument.
   + Don't use `abs()`. Use the flow from problem 1 and multiply by negative one as necessary. 
   
```{r}
abs_value <- function(num) {
  if (num < 0) {
    return(num*-1)
  } else {
    return(num)
  }
}
#Test
abs_value(-6)

```

5. Hard mode: add an error check to that function that prints out the string "Please pass a numerical value to this function" if the user passes the function a string. 
   + There are functions that check and return T/F: `is.numeric()` or `is.character()` would be relevant here
   
```{r}
abs_value <- function(num) {
  if(!is.numeric(num)){
    print("Please pass a numerical value to this function")
    return(NULL)
  }
  if (num < 0) {
    return(num*-1)
  } else {
    return(num)
  }
}
#Test
abs_value("abc")

```
   
   






```

